---
title: "Penguins_ANOVA"
author: "Kelly Odion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Loag packages and read in the penguins.csv data 
```{r, include = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our question: 

1. Is there a significant difference in mean flipper length for femal penguins by species,
(Chinstrap, Gentoo, and Adelie)?

2. Do some exploring 

New functions: with + table for easy counting over multiple factors

Update species name using case_when 

```{r}
counts <- with(penguins, table(species, sex))
View(counts)

penguins2 <- penguins %>% 
  mutate(common_name = case_when(species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap", 
                                 species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo", 
                                 species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie")) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")
penguins2
```

- Exploratory graphs 
- Summary statistics 
- Levene's tests for equal variances
```{r}
hists <- ggplot(penguins2, aes(x = flipper_length)) + 
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~common_name)

hists


quant <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~ common_name)
quant

# Levene's test for equal variances (>2 groups..if you have two groups, use the F-test for equal variances)

#We'll use the function leveneTest from the 'car' package

#H0: Variances are equal 
#HA: Variances are not equal 

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene

#We retain the null hypothesis of equal variances (p = 0.06)

penguin_var <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(variances = var(flipper_length))

penguin_var
```

#3. One-way ANOVA

Single factor: common_name
Number of levels: 3 (Chinstrap, Gentoo, Adelie)
Random Variable: flipper_length (mm) 

Is there a signficant difference in mean flipper length (mm) for female Chinstrap, Gentoo, and Adelie penguins? 

```{r}
#H0: The means are equal 
#Ha: At least one pair of means is not equal(at LEAST two means differ significantly)

penguin_aov <- aov(flipper_length ~ common_name, data = penguins2)

summary(penguin_aov)

#if we take samples from these populations and they acutally have the same mean, then there is a very very small chance that we could have taken these samples and gotten means as different as we did. Which ones are different? All three are different from each other? Or something else?

#Post-hoc testing using Tukey's HSD

penguin_ph <- TukeyHSD(penguin_aov)
penguin_ph
```

Mean flipper lengths for Adelie, Gentoo, and Chinstrap penguins are all significantly different (F(df) = statistic, p <0.001, alpha= 0.05 with post-hoc Tukey's HSD, $\alpha = 0.05$, 
