---
title: "Penguins_ANOVA"
author: "Kelly Odion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Loag packages and read in the penguins.csv data 
```{r, include = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our question: 

1. Is there a significant difference in mean flipper length for femal penguins by species,
(Chinstrap, Gentoo, and Adelie)?

2. Do some exploring 

New functions: with + table for easy counting over multiple factors

Update species name using case_when 

```{r}
counts <- with(penguins, table(species, sex))
View(counts)

penguins2 <- penguins %>% 
  mutate(common_name = case_when(species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap", 
                                 species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo", 
                                 species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie")) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")
penguins2
```

- Exploratory graphs 
- Summary statistics 
- Levene's tests for equal variances
```{r}
hists <- ggplot(penguins2, aes(x = flipper_length)) + 
  geom_histogram(aes(fill = common_name))

hists
```

